---
title             : "The subjective experience of O*NET work experiences as demands and resources"
shorttitle        : "Title"

author: 
  - name          : "Alicia Stachowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Menomenie, WI"
    email         : "stachowskia@uwstout.edu"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "2"
  - name          : "John Kulas"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin - Stout"
  - id            : "2"
    institution   : "Montclair State University"

abstract: |
  O*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource. 
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

  The job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] have inspired a plethora a study on the process and experience of job stress and employee motivation in recent decades. In the current project, we draw attention to a basic question regarding a key assumption we make regarding this process - that of the objective nature of job characteristics as either demands or resources. The major contribution of this project is to document whether job context and characteristics (pulled from O*Net) can simultaneously be classified as resources and as demands. We further present descriptive information regarding which job context and characteristics are rated the highest across jobs.
  
## The Job demands-Resources Theory

The job demands-resources theory is an extension of the well-known job demands-resources model put forth by Demerouti and colleagues in 2001 [@demerouti2001job]. The job demands-resources model had been so heavily studied that a number of meta-analyses have been possible (e.g., [@crawford2010linking];
[@halbesleben2010meta]; [@nahrgang2011safety]). The theory generated by the model integrates both the job design and job stress literatures to help explain the conditions under which a job would result in employee stress vs. motivation [@bakker2014job]. Per the job demands-resources theory, both work environment and job characteristics can be modeled via job demands and resources. @demerouti2001job define job demands broadly as components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand). Resources, on the other hand, are physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job].
  Experiencing an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (demands) or motivation (resources; [@bakker2014job]. Job characteristics perceived to be demanding are effortful are frequently associated with negative outcomes such as exhaustion [e.g., @bakker2003dual]. On the other hand, job characteristics perceived as resources (fulfil psychological needs) are associated with positive organizational outcomes like engagement and motivation [@bakker2007job]. 
  
## Objective vs. Subjective Nature of Demands and Resources: The Role of Appraisal
  @searle2015merits note that the majority of the research on workplace demands is based on apriori classifications of demands. However, the stress experience, or process, described early on by @lazarus1984stress is grounded in the assumption that individual appraisals of stressors/demands vary. Their transactional theory or stress and coping states that people continuously appraise stimuli in their environments. An appraisal is the cognitive process whereby meaning is assigned to a stimulus. If a stimulus is appraised as a stressor (threat, challenge, potentially harmful), emotional distress leads to coping of some kind. This action to cope is also associated with another appraisal about the outcome itself and the process continues if the outcomes is not appraised as favorable [@lazarus1984stress]. The stress appraisal process suggests that classifying a job characteristic or environmental condition as an objective demand or resource might be in error. 
  We next consider the (limited) empirical evidence on this topic. First, some relatively recent research suggests that job demands and resources may not be universally appraised or assigned as such. Starting with job demands, @webster2011extending, for example, studied workload, role ambiguity, and role conflict demands, and found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees. While their study did include resources, it nonetheless points to individual difference on how people perceive stressors at work. Although part of a much larger study on retirement, @sonnega_comparison_2018 compared self-reported (subjective) ratings of degree of physical demand, stress, and need for intense concentration from the Health and Retirement Study with objective ratings from O*Net. Correlations physical demand (r = .52), stress (r = .10), and need for intense concentration (r = .14), again suggesting perhaps that our objective ratings of job demands (and resources) may be subject to a greater level of individual difference than assumed. Next considering resources, @schmitz_interpreting_2019 captured subjective and objective resources in their study of retirement also. Correlations of composite variables for the resources of autonomy (r = .12), recognition of work (r = .07), decision freedom (r = .08), and advancement (r = -.01), while significant, certainly do not reflect high levels of overlap. 
  We do acknowledge as well, that demands and resources are not necessarily consistent across days, or seasons, for many employees. @downes2021incorporating meta-analysis addresses this reality in depth, although it is beyond the scope of this project. 
  
## Current Study and Hypotheses

  The current study aims to explore the degree to which job context and job characteristic items from O*Net are considered demands and resources. Given theoretical and empirical findings, it seems quite plausible that our apriori assignment of job elements to a “demand” or “resource” category may be too simplistic. We aim to document a list of the highest rated demands and resources, as well as information on overlap of job characteristics as demands and resources, in addition to addressing the following predictions.
  
>*Hypothesis 1*: There is 


## Current Study and Research Questions for other studies + notes

@bakker2017job state that, "...research has shown that challenge demands may be experienced as hindrance demands (and vice versa) depending on the context" (p. 278). We extend this acknowlegement by investigating whether some characteristics of work may also vacillate between demand and *resource*. 

# Study 2 Introduction: Correlates with Engagement and Stress

  Research on the job demands-resources model [@demerouti2001job] and later job demands-resources theory [@bakker2017job] highlight the importance of work characteristics on the experience of motivation and strain, which clearly have an impact on job performance. In this paper, we extend this critical research to that of the distinction between challenge and hinderance demands (and resource) in the workplace, and how they relate to two important organizational outcomes: engagement and stress. Prior to presenting the current study in detail, we provide a brief overview of the relevant theories and relevant empirical work on this topic. 
  
## The Job demands-Resources Theory  

  The overarching context for this study is that of the job demands-resources theory, which is an expansion of the well-studied job demands-resources model [@demerouti2001job]. One of the major advantages of the job demands-resources theory is that it allows us to model both work environment and job characteristics via job resources and demands. *Resources* include physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. In contrast, demands include components of a job that require sustained effort, and as such, produce psychological or physiological strain (e.g., high work pressure is frequently cited as a common demand; @demerouti2001job). 

  Cognitively, the perception of an element of one’s job as a resource or demand activates one of two distinct processes: either health impairment (resulting from demands) or motivation (resulting from resources) [@bakker2014job]. Pertinent to the current study, demanding job characteristics are frequently often associated with negative outcomes [e.g., @bakker2003dual], whereas job characteristics deemed resources have been associated with positive organizational outcomes like engagement and motivation [@bakker2007job]. 
  
## The Essential Role of Appraisal  

  As implied in the last paragraph, job context and characteristics are “assigned” or appraised as demands or resources. Although some research on job demands in particular is based on apriori classifications of demands [@searle2015merits], the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive being a public figure as a resource or as a demand. The stress process speaks to how such individual difference in appraisal is possible. @lazarus1984stress presented the transactional theory of stress and coping, which states that people cognitively appraise stimuli in their environments on a continuous basis. Via this process, meaning is assigned to stimuli – if appraised as threatening, challenging, or possibly harmful, the resulting emotional distress initiates coping. The cycle of appraisal then continues based on the action to cope with the stressor [@lazarus1984stress]. 
  
## The Challenge-Hinderance Framework  

  Although there is a tendency to attach a negative connotation to the word “stress”, @selye1936syndrome defined stress as a response to change, which is quite non-specific. We return to the employed public figure for this next section. It is quite probable that two employees would be called upon to serve as a spokesperson for their organization in a time of need. One may appraise the circumstance as an opportunity to positively influence others, while the other may plausibly feel paralyzed by the task. @cavanaugh2000empirical delineated between two forms of demands – that of *challenge* and *hinderance* demands. Challenge demands promote mastery, personal growth, and future gains. Hinderance demands, in contrast, inhibit growth, learning and goal achievement. This particular distinction has been of value in determining what demands are related to various outcomes, whereby challenge stressors are typically associated with positive outcomes, and hinderance stressors, negative outcomes (e.g., @cavanaugh2000empirical). However, one of the key questions we need to ask as researchers pertains to the very basic consideration of appraisals.
  
  We next consider the empirical evidence on this topic. The first obvious question is whether people perceive demands and challenges vs. hinderances, or whether all demands are under a larger “demands” category. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as challenges or hindrances demands, they could also simultaneously be perceived as being both a challenge and hinderance to different degrees. While their study did include resources, it nonetheless points to the possibility that demands might be differentially appraised. @cavanaugh2000empirical, in a study of managers, found that challenge demands were positively related to job satisfaction and negatively related to job search behaviors, while hinderance demands demonstrated the opposite pattern. 
  
### Notes on which other studies to read and add next  

@bakker2013weekly Weekly work engagement and flourishing: The role of
hindrance and challenge job demands
@ crawford2010linking  Crawford, E. R., Lepine, J. A., & Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. The Journal of Applied Psychology, 95(5), 834–48. doi:10.1037/a0019364
@ lepine2004challenge LePine, J. A., LePine, M. A., & Jackson, C. L. (2004). Challenge and hindrance stress: relationships with exhaustion, motivation to learn, and learning performance. The Journal of Applied Psychology, 89(5), 883–91. doi:10.1037/0021-9010.89.5.883
@podsakoff2007differential  Podsakoff, N. P., LePine, J. A., & LePine, M. A. (2007). Differential challenge stressorhindrance stressor relationships with job attitudes, turnover intentions, turnover, and 43 withdrawal behavior: a meta-analysis. The Journal of Applied Psychology, 92(2), 438–54. doi:10.1037/0021-9010.92.2.438
Look at the resources in the following paper as well:
@o2019so O'Brien, K. E., & Beehr, T. A. (2019). So far, so good: Up to now, the challenge–hindrance framework describes a practical and accurate distinction. Journal of Organizational Behavior, 40(8), 962-972.

## Current Study and Hypotheses  

  Given the abundance of theoretical and empirical support for the connection between resources and positive organizational outcomes (cites), and between demands and negative resources, we sought to explore whether or not the appraisal of a demand as a challenge or hinderance would be related *differently* to two organizational outcomes: engagement DEFINE THESE (a positive affective experience) and workplace stress (a negative affective experience). Drawing on the job demands-resources theory we propose that job elements appraised as “challenge demands” (i.e., promote mastery, personal growth, and future gains) would activate (be related to) a positive state – that of engagement. In contrast, elements of one’s job appraised as a hinderance demand (i.e., inhibit growth, learning and goal achievement) would activate a negative state – here, stress.  
Hypothesis 1a: Job characteristics appraised as resources will be positively associated with engagement. 


>*Hypothesis 1b*: Job characteristics appraised as resources will be negatively associated with stress.

>*Hypothesis 2a*: Job characteristics appraised as challenge demands will be positively associated with engagement. 

>*Hypothesis 2b*: Job characteristics appraised as challenge demands will be negatively associated with stress.

>*Hypothesis 3a*: Job characteristics appraised as hinderance demands will be negatively associated with engagement. 

>*Hypothesis 3b*: Job characteristics appraised as hinderance demands will be positively associated with stress.

# Methods

## Study 1  

top 15 demands and resources, divided by skilled versus knowledge workers, 

## Study 2  

burnout and stress components (correlations), 

## Study 3

integration of JDR with O*Net categories (morphs into descriptives). 

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants  



## Material  

Job Characteristics (O*Net)
Job Resources
Job Demands (Hinderance and Challenge)
Stress: Copenhagen Psychosocial Questionnaire
Engagement
Demographics 
## Procedure  

Qualtrics panel

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
