---
title             : "O*NET defined demands and resources and associations with stress, burnout, and engagement"
shorttitle        : "Title"

author: 
  - name          : "Alicia Stachowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Menomenie, WI"
    email         : "stachowskia@uwstout.edu"
  - name          : "Renata Garcia Prieto Palacios Roji"
    affiliation   : "2"
  - name          : "John Kulas"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "University of Wisconsin - Stout"
  - id            : "2"
    institution   : "Montclair State University"

abstract: |
  O*NET work characteristics were rated in terms of relevance, perception of demand, and perception as resource. 
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "jdr.bib", "jobdemands_resources_bibtex.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
```


```{r study1}

temp <- read.csv("initial_data_screen.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

x <- paste("item", sep="",1:404)
y <- t(temp[2,])
                                        ## decluttering Qualtrics excess
data <- temp[-c(1:3),]                                           ## Getting rid of all 3 weird Qualtrics rows
colnames(data) <- x

incomplete <- read.csv("inprogress.csv", header=FALSE, na.strings="")   ## NOTE: 404 vars (9/28/21) make sure to check indexing used throughout script

data2 <- incomplete[-c(1:2),-c(10,12,16,113,199,285,371,379,400, 406:411)]                                          

data3 <- as.data.frame(cbind(data2$V8,data2$V9,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2$V1,data2))

colnames(data3) <- x

rm(x, y, temp)       

use <- rbind(data,data3)

## STILL NEED FILE WITH BAD RESPONDENTS IDENTIFIED (E.G., Item_18=2, na > 200, longstring > 20, CARELESS CHECKS > 1)

library(careless)
use$careless_long <- longstring(use[18:399])
use$missing <- rowSums(is.na(use[18:404])) 

different <- use[ which(use$item18 == 2 | use$careless_long > 20 | use$missing > 200), ]

attention <- use[which(use$item61 == 5 & use$item145 == 5 & use$item248 == 2 & use$item308 == 3), ]

data <- data.frame(lapply(attention, function(x) as.numeric(as.character(x))))
data <- data[,c(1:404)]

numtot <- nrow(use)
numkicked <- nrow(different)
numvalid <- nrow(data)

```

```{r demos}

a <- descr::freq(use$item401, plot=FALSE)

use$item402[use$item402 == "Female " | use$item402 == "female" | use$item402 == "FEMALE" | use$item402 == "Woman" | use$item402 == "Mujer" | use$item402 == "feminine" | use$item402 == "fEMALE" | use$item402 == "F" | use$item402 == "Femenale" | use$item402 == "feminino" | use$item402 == "female " | use$item402 == "Fem" | use$item402 == "Feminine" | use$item402 == "feminine" | use$item402 == "WOMAN" | use$item402 == "Femal" | use$item402 == "femenine" | use$item402 == "Femenine" | use$item402 == "femenino" | use$item402 == "woman"]  <- "Female"

use$item402[use$item402 == "gerente" | use$item402 == "M" | use$item402 == "Make" | use$item402 == "Mal" | use$item402 == "male" | use$item402 == "MALE" | use$item402 == "male" | use$item402 == "Male" | use$item402 == "mals" | use$item402 == "man" | use$item402 == "masculine" | use$item402 == "Masculine" | use$item402 == "Man" | use$item402 == "mals " | use$item402 == "male " | use$item402 == "Male "]  <- "Male"

b <- descr::freq(use$item402, plot=FALSE)

##Job title
library(labourR)


#ESCO/ISCO classification using the labourR package
#ISCO = International Standard Classification of Occupations

attention$id <- 1:nrow(attention) #adds unique identifier to satisfy inane requirement of classify_occupation()

ISCO <- classify_occupation(attention, text_col = 'item400', isco_level = 1) 

m3 <-merge(attention, ISCO, by.x = "id", by.y = "id", all.x = TRUE)

c <- descr::freq(m3$preferredLabel, plot=FALSE)

knowledge <- data[ which(m3$iscoGroup == "1" | m3$iscoGroup == "2"), ]
service <- data[ which(m3$iscoGroup == "3" | m3$iscoGroup == "4" | m3$iscoGroup == "5" | m3$iscoGroup == "6" | m3$iscoGroup == "7" | m3$iscoGroup == "8" | m3$iscoGroup == "9"), ]

data$item403[data$item403 == 2000]  <- 20

```

```{r generalrecodes}
## Qualtrics data all messed up

data$item82[data$item82 == 8]  <- 1
data$item82[data$item82 == 9]  <- 2
data$item82[data$item82 == 10] <- 3
data$item82[data$item82 == 11] <- 4
data$item82[data$item82 == 12] <- 5

data$item118[data$item118 == 9]  <- 1
data$item118[data$item118 == 10] <- 2
data$item118[data$item118 == 11] <- 3
data$item118[data$item118 == 12] <- 4
data$item118[data$item118 == 13] <- 5

data$item119[data$item119 == 11] <- 1
data$item119[data$item119 == 12] <- 2
data$item119[data$item119 == 13] <- 3
data$item119[data$item119 == 14] <- 4
data$item119[data$item119 == 15] <- 5

data$item120[data$item120 == 6]  <- 1
data$item120[data$item120 == 7]  <- 2
data$item120[data$item120 == 8]  <- 3
data$item120[data$item120 == 9]  <- 4
data$item120[data$item120 == 10] <- 5

data$item121[data$item121 == 6]  <- 1
data$item121[data$item121 == 7]  <- 2
data$item121[data$item121 == 8]  <- 3
data$item121[data$item121 == 9]  <- 4
data$item121[data$item121 == 10] <- 5

data$item122[data$item122 == 6]  <- 1
data$item122[data$item122 == 7]  <- 2
data$item122[data$item122 == 8]  <- 3
data$item122[data$item122 == 9]  <- 4
data$item122[data$item122 == 10] <- 5

data$item123[data$item123 == 6]  <- 1
data$item123[data$item123 == 7]  <- 2
data$item123[data$item123 == 8]  <- 3
data$item123[data$item123 == 9]  <- 4
data$item123[data$item123 == 10] <- 5

data$item124[data$item124 == 6]  <- 1
data$item124[data$item124 == 7]  <- 2
data$item124[data$item124 == 8]  <- 3
data$item124[data$item124 == 9]  <- 4
data$item124[data$item124 == 10] <- 5

data$item125[data$item125 == 6]  <- 1
data$item125[data$item125 == 7]  <- 2
data$item125[data$item125 == 8]  <- 3
data$item125[data$item125 == 9]  <- 4
data$item125[data$item125 == 10] <- 5

data$item126[data$item126 == 11]  <- 1
data$item126[data$item126 == 12]  <- 2
data$item126[data$item126 == 13]  <- 3
data$item126[data$item126 == 14]  <- 4
data$item126[data$item126 == 15]  <- 5

data$item127[data$item127 == 4]  <- 1
data$item127[data$item127 == 5]  <- 2
data$item127[data$item127 == 6]  <- 3
data$item127[data$item127 == 7]  <- 4
data$item127[data$item127 == 8]  <- 5

data$item128[data$item128 == 11]  <- 1
data$item128[data$item128 == 12]  <- 2
data$item128[data$item128 == 13]  <- 3
data$item128[data$item128 == 14]  <- 4
data$item128[data$item128 == 15]  <- 5

data$item129[data$item129 == 11]  <- 1
data$item129[data$item129 == 12]  <- 2
data$item129[data$item129 == 13]  <- 3
data$item129[data$item129 == 14]  <- 4
data$item129[data$item129 == 15]  <- 5

data$item130[data$item130 == 11]  <- 1
data$item130[data$item130 == 12]  <- 2
data$item130[data$item130 == 13]  <- 3
data$item130[data$item130 == 14]  <- 4
data$item130[data$item130 == 15]  <- 5

data$item131[data$item131 == 11]  <- 1
data$item131[data$item131 == 12]  <- 2
data$item131[data$item131 == 13]  <- 3
data$item131[data$item131 == 14]  <- 4
data$item131[data$item131 == 15]  <- 5

data$item132[data$item132 == 11]  <- 1
data$item132[data$item132 == 12]  <- 2
data$item132[data$item132 == 13]  <- 3
data$item132[data$item132 == 14]  <- 4
data$item132[data$item132 == 15]  <- 5

data$item133[data$item133 == 11]  <- 1
data$item133[data$item133 == 12]  <- 2
data$item133[data$item133 == 13]  <- 3
data$item133[data$item133 == 14]  <- 4
data$item133[data$item133 == 15]  <- 5

data$item134[data$item134 == 11]  <- 1
data$item134[data$item134 == 12]  <- 2
data$item134[data$item134 == 13]  <- 3
data$item134[data$item134 == 14]  <- 4
data$item134[data$item134 == 15]  <- 5

data$item135[data$item135 == 6]  <- 1
data$item135[data$item135 == 7]  <- 2
data$item135[data$item135 == 8]  <- 3
data$item135[data$item135 == 9]  <- 4
data$item135[data$item135 == 10] <- 5

data$item136[data$item136 == 6]  <- 1
data$item136[data$item136 == 7]  <- 2
data$item136[data$item136 == 8]  <- 3
data$item136[data$item136 == 9]  <- 4
data$item136[data$item136 == 10] <- 5

data$item137[data$item137 == 6]  <- 1
data$item137[data$item137 == 7]  <- 2
data$item137[data$item137 == 8]  <- 3
data$item137[data$item137 == 9]  <- 4
data$item137[data$item137 == 10] <- 5

data$item138[data$item138 == 16]  <- 1
data$item138[data$item138 == 17]  <- 2
data$item138[data$item138 == 18]  <- 3
data$item138[data$item138 == 19]  <- 4
data$item138[data$item138 == 20]  <- 5

data$item139[data$item139 == 6]  <- 1
data$item139[data$item139 == 7]  <- 2
data$item139[data$item139 == 8]  <- 3
data$item139[data$item139 == 9]  <- 4
data$item139[data$item139 == 10] <- 5

data$item140[data$item140 == 6]  <- 1
data$item140[data$item140 == 7]  <- 2
data$item140[data$item140 == 8]  <- 3
data$item140[data$item140 == 9]  <- 4
data$item140[data$item140 == 10] <- 5

data$item141[data$item141 == 6]  <- 1
data$item141[data$item141 == 7]  <- 2
data$item141[data$item141 == 8]  <- 3
data$item141[data$item141 == 9]  <- 4
data$item141[data$item141 == 10] <- 5

data$item142[data$item142 == 6]  <- 1
data$item142[data$item142 == 7]  <- 2
data$item142[data$item142 == 8]  <- 3
data$item142[data$item142 == 9]  <- 4
data$item142[data$item142 == 10] <- 5

data$item143[data$item143 == 6]  <- 1
data$item143[data$item143 == 7]  <- 2
data$item143[data$item143 == 8]  <- 3
data$item143[data$item143 == 9]  <- 4
data$item143[data$item143 == 10] <- 5

data$item144[data$item144 == 6]  <- 1
data$item144[data$item144 == 7]  <- 2
data$item144[data$item144 == 8]  <- 3
data$item144[data$item144 == 9]  <- 4
data$item144[data$item144 == 10] <- 5

## Attention check = 145

data$item146[data$item146 == 16]  <- 1
data$item146[data$item146 == 17]  <- 2
data$item146[data$item146 == 18]  <- 3
data$item146[data$item146 == 19]  <- 4
data$item146[data$item146 == 20]  <- 5

data$item147[data$item147 == 6]  <- 1
data$item147[data$item147 == 7]  <- 2
data$item147[data$item147 == 8]  <- 3
data$item147[data$item147 == 9]  <- 4
data$item147[data$item147 == 10] <- 5

data$item148[data$item148 == 6]  <- 1
data$item148[data$item148 == 7]  <- 2
data$item148[data$item148 == 8]  <- 3
data$item148[data$item148 == 9]  <- 4
data$item148[data$item148 == 10] <- 5

data$item149[data$item149 == 6]  <- 1
data$item149[data$item149 == 7]  <- 2
data$item149[data$item149 == 8]  <- 3
data$item149[data$item149 == 9]  <- 4
data$item149[data$item149 == 10] <- 5

data$item150[data$item150 == 11]  <- 1
data$item150[data$item150 == 12]  <- 2
data$item150[data$item150 == 13]  <- 3
data$item150[data$item150 == 14]  <- 4
data$item150[data$item150 == 15]  <- 5

data$item151[data$item151 == 11]  <- 1
data$item151[data$item151 == 12]  <- 2
data$item151[data$item151 == 13]  <- 3
data$item151[data$item151 == 14]  <- 4
data$item151[data$item151 == 15]  <- 5

data$item152[data$item152 == 11]  <- 1
data$item152[data$item152 == 12]  <- 2
data$item152[data$item152 == 13]  <- 3
data$item152[data$item152 == 14]  <- 4
data$item152[data$item152 == 15]  <- 5

data$item153[data$item153 == 11]  <- 1
data$item153[data$item153 == 12]  <- 2
data$item153[data$item153 == 13]  <- 3
data$item153[data$item153 == 14]  <- 4
data$item153[data$item153 == 15]  <- 5

data$item154[data$item154 == 11]  <- 1
data$item154[data$item154 == 12]  <- 2
data$item154[data$item154 == 13]  <- 3
data$item154[data$item154 == 14]  <- 4
data$item154[data$item154 == 15]  <- 5

data$item155[data$item155 == 11]  <- 1
data$item155[data$item155 == 12]  <- 2
data$item155[data$item155 == 13]  <- 3
data$item155[data$item155 == 14]  <- 4
data$item155[data$item155 == 15]  <- 5

data$item156[data$item156 == 11]  <- 1
data$item156[data$item156 == 12]  <- 2
data$item156[data$item156 == 13]  <- 3
data$item156[data$item156 == 14]  <- 4
data$item156[data$item156 == 15]  <- 5

data$item157[data$item157 == 11]  <- 1
data$item157[data$item157 == 12]  <- 2
data$item157[data$item157 == 13]  <- 3
data$item157[data$item157 == 14]  <- 4
data$item157[data$item157 == 15]  <- 5

data$item158[data$item158 == 6]  <- 1
data$item158[data$item158 == 7]  <- 2
data$item158[data$item158 == 8]  <- 3
data$item158[data$item158 == 9]  <- 4
data$item158[data$item158 == 10] <- 5

data$item159[data$item159 == 11]  <- 1
data$item159[data$item159 == 12]  <- 2
data$item159[data$item159 == 13]  <- 3
data$item159[data$item159 == 14]  <- 4
data$item159[data$item159 == 15]  <- 5

data$item160[data$item160 == 11]  <- 1
data$item160[data$item160 == 12]  <- 2
data$item160[data$item160 == 13]  <- 3
data$item160[data$item160 == 14]  <- 4
data$item160[data$item160 == 15]  <- 5

data$item161[data$item161 == 6]  <- 1
data$item161[data$item161 == 7]  <- 2
data$item161[data$item161 == 8]  <- 3
data$item161[data$item161 == 9]  <- 4
data$item161[data$item161 == 10] <- 5

data$item162[data$item162 == 11]  <- 1
data$item162[data$item162 == 12]  <- 2
data$item162[data$item162 == 13]  <- 3
data$item162[data$item162 == 14]  <- 4
data$item162[data$item162 == 15]  <- 5

data$item163[data$item163 == 11]  <- 1
data$item163[data$item163 == 12]  <- 2
data$item163[data$item163 == 13]  <- 3
data$item163[data$item163 == 14]  <- 4
data$item163[data$item163 == 15]  <- 5

data$item164[data$item164 == 11]  <- 1
data$item164[data$item164 == 12]  <- 2
data$item164[data$item164 == 13]  <- 3
data$item164[data$item164 == 14]  <- 4
data$item164[data$item164 == 15]  <- 5

data$item165[data$item165 == 11]  <- 1
data$item165[data$item165 == 12]  <- 2
data$item165[data$item165 == 13]  <- 3
data$item165[data$item165 == 14]  <- 4
data$item165[data$item165 == 15]  <- 5

data$item166[data$item166 == 11]  <- 1
data$item166[data$item166 == 12]  <- 2
data$item166[data$item166 == 13]  <- 3
data$item166[data$item166 == 14]  <- 4
data$item166[data$item166 == 15]  <- 5

data$item167[data$item167 == 18]  <- 1
data$item167[data$item167 == 19]  <- 2
data$item167[data$item167 == 20]  <- 3
data$item167[data$item167 == 21]  <- 4
data$item167[data$item167 == 22]  <- 5

data$item168[data$item168 == 11]  <- 1
data$item168[data$item168 == 12]  <- 2
data$item168[data$item168 == 13]  <- 3
data$item168[data$item168 == 14]  <- 4
data$item168[data$item168 == 15]  <- 5

data$item169[data$item169 == 11]  <- 1
data$item169[data$item169 == 12]  <- 2
data$item169[data$item169 == 13]  <- 3
data$item169[data$item169 == 14]  <- 4
data$item169[data$item169 == 15]  <- 5

data$item170[data$item170 == 11]  <- 1
data$item170[data$item170 == 12]  <- 2
data$item170[data$item170 == 13]  <- 3
data$item170[data$item170 == 14]  <- 4
data$item170[data$item170 == 15]  <- 5

data$item171[data$item171 == 11]  <- 1
data$item171[data$item171 == 12]  <- 2
data$item171[data$item171 == 13]  <- 3
data$item171[data$item171 == 14]  <- 4
data$item171[data$item171 == 15]  <- 5

data$item172[data$item172 == 11]  <- 1
data$item172[data$item172 == 12]  <- 2
data$item172[data$item172 == 13]  <- 3
data$item172[data$item172 == 14]  <- 4
data$item172[data$item172 == 15]  <- 5

data$item173[data$item173 == 11]  <- 1
data$item173[data$item173 == 12]  <- 2
data$item173[data$item173 == 13]  <- 3
data$item173[data$item173 == 14]  <- 4
data$item173[data$item173 == 15]  <- 5

data$item174[data$item174 == 11]  <- 1
data$item174[data$item174 == 12]  <- 2
data$item174[data$item174 == 13]  <- 3
data$item174[data$item174 == 14]  <- 4
data$item174[data$item174 == 15]  <- 5

data$item175[data$item175 == 11]  <- 1
data$item175[data$item175 == 12]  <- 2
data$item175[data$item175 == 13]  <- 3
data$item175[data$item175 == 14]  <- 4
data$item175[data$item175 == 15]  <- 5

data$item176[data$item176 == 11]  <- 1
data$item176[data$item176 == 12]  <- 2
data$item176[data$item176 == 13]  <- 3
data$item176[data$item176 == 14]  <- 4
data$item176[data$item176 == 15]  <- 5

data$item177[data$item177 == 11]  <- 1
data$item177[data$item177 == 12]  <- 2
data$item177[data$item177 == 13]  <- 3
data$item177[data$item177 == 14]  <- 4
data$item177[data$item177 == 15]  <- 5

data$item178[data$item178 == 11]  <- 1
data$item178[data$item178 == 12]  <- 2
data$item178[data$item178 == 13]  <- 3
data$item178[data$item178 == 14]  <- 4
data$item178[data$item178 == 15]  <- 5

data$item179[data$item179 == 11]  <- 1
data$item179[data$item179 == 12]  <- 2
data$item179[data$item179 == 13]  <- 3
data$item179[data$item179 == 14]  <- 4
data$item179[data$item179 == 15]  <- 5

data$item180[data$item180 == 11]  <- 1
data$item180[data$item180 == 12]  <- 2
data$item180[data$item180 == 13]  <- 3
data$item180[data$item180 == 14]  <- 4
data$item180[data$item180 == 15]  <- 5

data$item181[data$item181 == 11]  <- 1
data$item181[data$item181 == 12]  <- 2
data$item181[data$item181 == 13]  <- 3
data$item181[data$item181 == 14]  <- 4
data$item181[data$item181 == 15]  <- 5

data$item182[data$item182 == 11]  <- 1
data$item182[data$item182 == 12]  <- 2
data$item182[data$item182 == 13]  <- 3
data$item182[data$item182 == 14]  <- 4
data$item182[data$item182 == 15]  <- 5

data$item183[data$item183 == 11]  <- 1
data$item183[data$item183 == 12]  <- 2
data$item183[data$item183 == 13]  <- 3
data$item183[data$item183 == 14]  <- 4
data$item183[data$item183 == 15]  <- 5

data$item184[data$item184 == 21]  <- 1
data$item184[data$item184 == 22]  <- 2
data$item184[data$item184 == 23]  <- 3
data$item184[data$item184 == 24]  <- 4
data$item184[data$item184 == 25]  <- 5

data$item185[data$item185 == 11]  <- 1
data$item185[data$item185 == 12]  <- 2
data$item185[data$item185 == 13]  <- 3
data$item185[data$item185 == 14]  <- 4
data$item185[data$item185 == 15]  <- 5

data$item186[data$item186 == 11]  <- 1
data$item186[data$item186 == 12]  <- 2
data$item186[data$item186 == 13]  <- 3
data$item186[data$item186 == 14]  <- 4
data$item186[data$item186 == 15]  <- 5

data$item187[data$item187 == 11]  <- 1
data$item187[data$item187 == 12]  <- 2
data$item187[data$item187 == 13]  <- 3
data$item187[data$item187 == 14]  <- 4
data$item187[data$item187 == 15]  <- 5

data$item188[data$item188 == 11]  <- 1
data$item188[data$item188 == 12]  <- 2
data$item188[data$item188 == 13]  <- 3
data$item188[data$item188 == 14]  <- 4
data$item188[data$item188 == 15]  <- 5

data$item189[data$item189 == 11]  <- 1
data$item189[data$item189 == 12]  <- 2
data$item189[data$item189 == 13]  <- 3
data$item189[data$item189 == 14]  <- 4
data$item189[data$item189 == 15]  <- 5

data$item190[data$item190 == 11]  <- 1
data$item190[data$item190 == 12]  <- 2
data$item190[data$item190 == 13]  <- 3
data$item190[data$item190 == 14]  <- 4
data$item190[data$item190 == 15]  <- 5

data$item191[data$item191 == 11]  <- 1
data$item191[data$item191 == 12]  <- 2
data$item191[data$item191 == 13]  <- 3
data$item191[data$item191 == 14]  <- 4
data$item191[data$item191 == 15]  <- 5

data$item192[data$item192 == 11]  <- 1
data$item192[data$item192 == 12]  <- 2
data$item192[data$item192 == 13]  <- 3
data$item192[data$item192 == 14]  <- 4
data$item192[data$item192 == 15]  <- 5

data$item193[data$item193 == 11]  <- 1
data$item193[data$item193 == 12]  <- 2
data$item193[data$item193 == 13]  <- 3
data$item193[data$item193 == 14]  <- 4
data$item193[data$item193 == 15]  <- 5

data$item194[data$item194 == 11]  <- 1
data$item194[data$item194 == 12]  <- 2
data$item194[data$item194 == 13]  <- 3
data$item194[data$item194 == 14]  <- 4
data$item194[data$item194 == 15]  <- 5

data$item195[data$item195 == 11]  <- 1
data$item195[data$item195 == 12]  <- 2
data$item195[data$item195 == 13]  <- 3
data$item195[data$item195 == 14]  <- 4
data$item195[data$item195 == 15]  <- 5

data$item196[data$item196 == 11]  <- 1
data$item196[data$item196 == 12]  <- 2
data$item196[data$item196 == 13]  <- 3
data$item196[data$item196 == 14]  <- 4
data$item196[data$item196 == 15]  <- 5

data$item197[data$item197 == 11]  <- 1
data$item197[data$item197 == 12]  <- 2
data$item197[data$item197 == 13]  <- 3
data$item197[data$item197 == 14]  <- 4
data$item197[data$item197 == 15]  <- 5

data$item198[data$item198 == 11]  <- 1
data$item198[data$item198 == 12]  <- 2
data$item198[data$item198 == 13]  <- 3
data$item198[data$item198 == 14]  <- 4
data$item198[data$item198 == 15]  <- 5

data$item199[data$item199 == 11]  <- 1
data$item199[data$item199 == 12]  <- 2
data$item199[data$item199 == 13]  <- 3
data$item199[data$item199 == 14]  <- 4
data$item199[data$item199 == 15]  <- 5

data$item200[data$item200 == 11]  <- 1
data$item200[data$item200 == 12]  <- 2
data$item200[data$item200 == 13]  <- 3
data$item200[data$item200 == 14]  <- 4
data$item200[data$item200 == 15]  <- 5

data$item201[data$item201 == 11]  <- 1
data$item201[data$item201 == 12]  <- 2
data$item201[data$item201 == 13]  <- 3
data$item201[data$item201 == 14]  <- 4
data$item201[data$item201 == 15]  <- 5

data$item202[data$item202 == 11]  <- 1
data$item202[data$item202 == 12]  <- 2
data$item202[data$item202 == 13]  <- 3
data$item202[data$item202 == 14]  <- 4
data$item202[data$item202 == 15]  <- 5

data$item203[data$item203 == 9]   <- 1
data$item203[data$item203 == 10]  <- 2
data$item203[data$item203 == 11]  <- 3
data$item203[data$item203 == 12]  <- 4
data$item203[data$item203 == 13]  <- 5

data$item204[data$item204 == 11]  <- 1
data$item204[data$item204 == 12]  <- 2
data$item204[data$item204 == 13]  <- 3
data$item204[data$item204 == 14]  <- 4
data$item204[data$item204 == 15]  <- 5

data$item205[data$item205 == 6]  <- 1
data$item205[data$item205 == 7]  <- 2
data$item205[data$item205 == 8]  <- 3
data$item205[data$item205 == 9]  <- 4
data$item205[data$item205 == 10] <- 5

data$item206[data$item206 == 6]  <- 1
data$item206[data$item206 == 7]  <- 2
data$item206[data$item206 == 8]  <- 3
data$item206[data$item206 == 9]  <- 4
data$item206[data$item206 == 10] <- 5

data$item207[data$item207 == 6]  <- 1
data$item207[data$item207 == 7]  <- 2
data$item207[data$item207 == 8]  <- 3
data$item207[data$item207 == 9]  <- 4
data$item207[data$item207 == 10] <- 5

data$item208[data$item208 == 6]  <- 1
data$item208[data$item208 == 7]  <- 2
data$item208[data$item208 == 8]  <- 3
data$item208[data$item208 == 9]  <- 4
data$item208[data$item208 == 10] <- 5

data$item209[data$item209 == 6]  <- 1
data$item209[data$item209 == 7]  <- 2
data$item209[data$item209 == 8]  <- 3
data$item209[data$item209 == 9]  <- 4
data$item209[data$item209 == 10] <- 5

data$item210[data$item210 == 6]  <- 1
data$item210[data$item210 == 7]  <- 2
data$item210[data$item210 == 8]  <- 3
data$item210[data$item210 == 9]  <- 4
data$item210[data$item210 == 10] <- 5

data$item211[data$item211 == 11]  <- 1
data$item211[data$item211 == 12]  <- 2
data$item211[data$item211 == 13]  <- 3
data$item211[data$item211 == 14]  <- 4
data$item211[data$item211 == 15]  <- 5

data$item212[data$item212 == 4]  <- 1
data$item212[data$item212 == 5]  <- 2
data$item212[data$item212 == 6]  <- 3
data$item212[data$item212 == 7]  <- 4
data$item212[data$item212 == 8]  <- 5

data$item213[data$item213 == 11]  <- 1
data$item213[data$item213 == 12]  <- 2
data$item213[data$item213 == 13]  <- 3
data$item213[data$item213 == 14]  <- 4
data$item213[data$item213 == 15]  <- 5

data$item214[data$item214 == 11]  <- 1
data$item214[data$item214 == 12]  <- 2
data$item214[data$item214 == 13]  <- 3
data$item214[data$item214 == 14]  <- 4
data$item214[data$item214 == 15]  <- 5

data$item215[data$item215 == 11]  <- 1
data$item215[data$item215 == 12]  <- 2
data$item215[data$item215 == 13]  <- 3
data$item215[data$item215 == 14]  <- 4
data$item215[data$item215 == 15]  <- 5

data$item216[data$item216 == 11]  <- 1
data$item216[data$item216 == 12]  <- 2
data$item216[data$item216 == 13]  <- 3
data$item216[data$item216 == 14]  <- 4
data$item216[data$item216 == 15]  <- 5

data$item217[data$item217 == 11]  <- 1
data$item217[data$item217 == 12]  <- 2
data$item217[data$item217 == 13]  <- 3
data$item217[data$item217 == 14]  <- 4
data$item217[data$item217 == 15]  <- 5

data$item218[data$item218 == 11]  <- 1
data$item218[data$item218 == 12]  <- 2
data$item218[data$item218 == 13]  <- 3
data$item218[data$item218 == 14]  <- 4
data$item218[data$item218 == 15]  <- 5

data$item219[data$item219 == 11]  <- 1
data$item219[data$item219 == 12]  <- 2
data$item219[data$item219 == 13]  <- 3
data$item219[data$item219 == 14]  <- 4
data$item219[data$item219 == 15]  <- 5

data$item220[data$item220 == 6]  <- 1
data$item220[data$item220 == 7]  <- 2
data$item220[data$item220 == 8]  <- 3
data$item220[data$item220 == 9]  <- 4
data$item220[data$item220 == 10] <- 5

data$item221[data$item221 == 6]  <- 1
data$item221[data$item221 == 7]  <- 2
data$item221[data$item221 == 8]  <- 3
data$item221[data$item221 == 9]  <- 4
data$item221[data$item221 == 10] <- 5

data$item222[data$item222 == 6]  <- 1
data$item222[data$item222 == 7]  <- 2
data$item222[data$item222 == 8]  <- 3
data$item222[data$item222 == 9]  <- 4
data$item222[data$item222 == 10] <- 5

data$item223[data$item223 == 16] <- 1
data$item223[data$item223 == 17] <- 2
data$item223[data$item223 == 18] <- 3
data$item223[data$item223 == 19] <- 4
data$item223[data$item223 == 20] <- 5

data$item224[data$item224 == 6]  <- 1
data$item224[data$item224 == 7]  <- 2
data$item224[data$item224 == 8]  <- 3
data$item224[data$item224 == 9]  <- 4
data$item224[data$item224 == 10] <- 5

data$item225[data$item225 == 6]  <- 1
data$item225[data$item225 == 7]  <- 2
data$item225[data$item225 == 8]  <- 3
data$item225[data$item225 == 9]  <- 4
data$item225[data$item225 == 10] <- 5

data$item226[data$item226 == 6]  <- 1
data$item226[data$item226 == 7]  <- 2
data$item226[data$item226 == 8]  <- 3
data$item226[data$item226 == 9]  <- 4
data$item226[data$item226 == 10] <- 5

data$item227[data$item227 == 6]  <- 1
data$item227[data$item227 == 7]  <- 2
data$item227[data$item227 == 8]  <- 3
data$item227[data$item227 == 9]  <- 4
data$item227[data$item227 == 10] <- 5

data$item228[data$item228 == 6]  <- 1
data$item228[data$item228 == 7]  <- 2
data$item228[data$item228 == 8]  <- 3
data$item228[data$item228 == 9]  <- 4
data$item228[data$item228 == 10] <- 5

data$item229[data$item229 == 6]  <- 1
data$item229[data$item229 == 7]  <- 2
data$item229[data$item229 == 8]  <- 3
data$item229[data$item229 == 9]  <- 4
data$item229[data$item229 == 10] <- 5

data$item230[data$item230 == 16] <- 1
data$item230[data$item230 == 17] <- 2
data$item230[data$item230 == 18] <- 3
data$item230[data$item230 == 19] <- 4
data$item230[data$item230 == 20] <- 5

data$item231[data$item231 == 6]  <- 1
data$item231[data$item231 == 7]  <- 2
data$item231[data$item231 == 8]  <- 3
data$item231[data$item231 == 9]  <- 4
data$item231[data$item231 == 10] <- 5

data$item232[data$item232 == 6]  <- 1
data$item232[data$item232 == 7]  <- 2
data$item232[data$item232 == 8]  <- 3
data$item232[data$item232 == 9]  <- 4
data$item232[data$item232 == 10] <- 5

data$item233[data$item233 == 6]  <- 1
data$item233[data$item233 == 7]  <- 2
data$item233[data$item233 == 8]  <- 3
data$item233[data$item233 == 9]  <- 4
data$item233[data$item233 == 10] <- 5

data$item234[data$item234 == 11]  <- 1
data$item234[data$item234 == 12]  <- 2
data$item234[data$item234 == 13]  <- 3
data$item234[data$item234 == 14]  <- 4
data$item234[data$item234 == 15]  <- 5

data$item235[data$item235 == 11]  <- 1
data$item235[data$item235 == 12]  <- 2
data$item235[data$item235 == 13]  <- 3
data$item235[data$item235 == 14]  <- 4
data$item235[data$item235 == 15]  <- 5

data$item236[data$item236 == 11]  <- 1
data$item236[data$item236 == 12]  <- 2
data$item236[data$item236 == 13]  <- 3
data$item236[data$item236 == 14]  <- 4
data$item236[data$item236 == 15]  <- 5

data$item237[data$item237 == 11]  <- 1
data$item237[data$item237 == 12]  <- 2
data$item237[data$item237 == 13]  <- 3
data$item237[data$item237 == 14]  <- 4
data$item237[data$item237 == 15]  <- 5

data$item238[data$item238 == 11]  <- 1
data$item238[data$item238 == 12]  <- 2
data$item238[data$item238 == 13]  <- 3
data$item238[data$item238 == 14]  <- 4
data$item238[data$item238 == 15]  <- 5

data$item239[data$item239 == 11]  <- 1
data$item239[data$item239 == 12]  <- 2
data$item239[data$item239 == 13]  <- 3
data$item239[data$item239 == 14]  <- 4
data$item239[data$item239 == 15]  <- 5

data$item240[data$item240 == 11]  <- 1
data$item240[data$item240 == 12]  <- 2
data$item240[data$item240 == 13]  <- 3
data$item240[data$item240 == 14]  <- 4
data$item240[data$item240 == 15]  <- 5

data$item241[data$item241 == 11]  <- 1
data$item241[data$item241 == 12]  <- 2
data$item241[data$item241 == 13]  <- 3
data$item241[data$item241 == 14]  <- 4
data$item241[data$item241 == 15]  <- 5

data$item242[data$item242 == 6]  <- 1
data$item242[data$item242 == 7]  <- 2
data$item242[data$item242 == 8]  <- 3
data$item242[data$item242 == 9]  <- 4
data$item242[data$item242 == 10] <- 5

data$item243[data$item243 == 11]  <- 1
data$item243[data$item243 == 12]  <- 2
data$item243[data$item243 == 13]  <- 3
data$item243[data$item243 == 14]  <- 4
data$item243[data$item243 == 15]  <- 5

data$item244[data$item244 == 11]  <- 1
data$item244[data$item244 == 12]  <- 2
data$item244[data$item244 == 13]  <- 3
data$item244[data$item244 == 14]  <- 4
data$item244[data$item244 == 15]  <- 5

data$item245[data$item245 == 6]  <- 1
data$item245[data$item245 == 7]  <- 2
data$item245[data$item245 == 8]  <- 3
data$item245[data$item245 == 9]  <- 4
data$item245[data$item245 == 10] <- 5

data$item246[data$item246 == 11]  <- 1
data$item246[data$item246 == 12]  <- 2
data$item246[data$item246 == 13]  <- 3
data$item246[data$item246 == 14]  <- 4
data$item246[data$item246 == 15]  <- 5

data$item247[data$item247 == 11]  <- 1
data$item247[data$item247 == 12]  <- 2
data$item247[data$item247 == 13]  <- 3
data$item247[data$item247 == 14]  <- 4
data$item247[data$item247 == 15]  <- 5

## Attention check

data$item249[data$item249 == 11]  <- 1
data$item249[data$item249 == 12]  <- 2
data$item249[data$item249 == 13]  <- 3
data$item249[data$item249 == 14]  <- 4
data$item249[data$item249 == 15]  <- 5

data$item250[data$item250 == 11]  <- 1
data$item250[data$item250 == 12]  <- 2
data$item250[data$item250 == 13]  <- 3
data$item250[data$item250 == 14]  <- 4
data$item250[data$item250 == 15]  <- 5

data$item251[data$item251 == 11]  <- 1
data$item251[data$item251 == 12]  <- 2
data$item251[data$item251 == 13]  <- 3
data$item251[data$item251 == 14]  <- 4
data$item251[data$item251 == 15]  <- 5

data$item252[data$item252 == 18]  <- 1
data$item252[data$item252 == 19]  <- 2
data$item252[data$item252 == 20]  <- 3
data$item252[data$item252 == 21]  <- 4
data$item252[data$item252 == 22]  <- 5

data$item253[data$item253 == 11]  <- 1
data$item253[data$item253 == 12]  <- 2
data$item253[data$item253 == 13]  <- 3
data$item253[data$item253 == 14]  <- 4
data$item253[data$item253 == 15]  <- 5

data$item254[data$item254 == 11]  <- 1
data$item254[data$item254 == 12]  <- 2
data$item254[data$item254 == 13]  <- 3
data$item254[data$item254 == 14]  <- 4
data$item254[data$item254 == 15]  <- 5

data$item255[data$item255 == 11]  <- 1
data$item255[data$item255 == 12]  <- 2
data$item255[data$item255 == 13]  <- 3
data$item255[data$item255 == 14]  <- 4
data$item255[data$item255 == 15]  <- 5

data$item256[data$item256 == 11]  <- 1
data$item256[data$item256 == 12]  <- 2
data$item256[data$item256 == 13]  <- 3
data$item256[data$item256 == 14]  <- 4
data$item256[data$item256 == 15]  <- 5

data$item257[data$item257 == 11]  <- 1
data$item257[data$item257 == 12]  <- 2
data$item257[data$item257 == 13]  <- 3
data$item257[data$item257 == 14]  <- 4
data$item257[data$item257 == 15]  <- 5

data$item258[data$item258 == 11]  <- 1
data$item258[data$item258 == 12]  <- 2
data$item258[data$item258 == 13]  <- 3
data$item258[data$item258 == 14]  <- 4
data$item258[data$item258 == 15]  <- 5

data$item259[data$item259 == 11]  <- 1
data$item259[data$item259 == 12]  <- 2
data$item259[data$item259 == 13]  <- 3
data$item259[data$item259 == 14]  <- 4
data$item259[data$item259 == 15]  <- 5

data$item260[data$item260 == 11]  <- 1
data$item260[data$item260 == 12]  <- 2
data$item260[data$item260 == 13]  <- 3
data$item260[data$item260 == 14]  <- 4
data$item260[data$item260 == 15]  <- 5

data$item261[data$item261 == 11]  <- 1
data$item261[data$item261 == 12]  <- 2
data$item261[data$item261 == 13]  <- 3
data$item261[data$item261 == 14]  <- 4
data$item261[data$item261 == 15]  <- 5

data$item262[data$item262 == 11]  <- 1
data$item262[data$item262 == 12]  <- 2
data$item262[data$item262 == 13]  <- 3
data$item262[data$item262 == 14]  <- 4
data$item262[data$item262 == 15]  <- 5

data$item263[data$item263 == 11]  <- 1
data$item263[data$item263 == 12]  <- 2
data$item263[data$item263 == 13]  <- 3
data$item263[data$item263 == 14]  <- 4
data$item263[data$item263 == 15]  <- 5

data$item264[data$item264 == 11]  <- 1
data$item264[data$item264 == 12]  <- 2
data$item264[data$item264 == 13]  <- 3
data$item264[data$item264 == 14]  <- 4
data$item264[data$item264 == 15]  <- 5

data$item265[data$item265 == 11]  <- 1
data$item265[data$item265 == 12]  <- 2
data$item265[data$item265 == 13]  <- 3
data$item265[data$item265 == 14]  <- 4
data$item265[data$item265 == 15]  <- 5

data$item266[data$item266 == 11]  <- 1
data$item266[data$item266 == 12]  <- 2
data$item266[data$item266 == 13]  <- 3
data$item266[data$item266 == 14]  <- 4
data$item266[data$item266 == 15]  <- 5

data$item267[data$item267 == 11]  <- 1
data$item267[data$item267 == 12]  <- 2
data$item267[data$item267 == 13]  <- 3
data$item267[data$item267 == 14]  <- 4
data$item267[data$item267 == 15]  <- 5

data$item268[data$item268 == 11]  <- 1
data$item268[data$item268 == 12]  <- 2
data$item268[data$item268 == 13]  <- 3
data$item268[data$item268 == 14]  <- 4
data$item268[data$item268 == 15]  <- 5

data$item269[data$item269 == 21]  <- 1
data$item269[data$item269 == 22]  <- 2
data$item269[data$item269 == 23]  <- 3
data$item269[data$item269 == 24]  <- 4
data$item269[data$item269 == 25]  <- 5

data$item270[data$item270 == 11]  <- 1
data$item270[data$item270 == 12]  <- 2
data$item270[data$item270 == 13]  <- 3
data$item270[data$item270 == 14]  <- 4
data$item270[data$item270 == 15]  <- 5

data$item271[data$item271 == 11]  <- 1
data$item271[data$item271 == 12]  <- 2
data$item271[data$item271 == 13]  <- 3
data$item271[data$item271 == 14]  <- 4
data$item271[data$item271 == 15]  <- 5

data$item272[data$item272 == 11]  <- 1
data$item272[data$item272 == 12]  <- 2
data$item272[data$item272 == 13]  <- 3
data$item272[data$item272 == 14]  <- 4
data$item272[data$item272 == 15]  <- 5

data$item273[data$item273 == 11]  <- 1
data$item273[data$item273 == 12]  <- 2
data$item273[data$item273 == 13]  <- 3
data$item273[data$item273 == 14]  <- 4
data$item273[data$item273 == 15]  <- 5

data$item274[data$item274 == 11]  <- 1
data$item274[data$item274 == 12]  <- 2
data$item274[data$item274 == 13]  <- 3
data$item274[data$item274 == 14]  <- 4
data$item274[data$item274 == 15]  <- 5

data$item275[data$item275 == 11]  <- 1
data$item275[data$item275 == 12]  <- 2
data$item275[data$item275 == 13]  <- 3
data$item275[data$item275 == 14]  <- 4
data$item275[data$item275 == 15]  <- 5

data$item276[data$item276 == 11]  <- 1
data$item276[data$item276 == 12]  <- 2
data$item276[data$item276 == 13]  <- 3
data$item276[data$item276 == 14]  <- 4
data$item276[data$item276 == 15]  <- 5

data$item277[data$item277 == 11]  <- 1
data$item277[data$item277 == 12]  <- 2
data$item277[data$item277 == 13]  <- 3
data$item277[data$item277 == 14]  <- 4
data$item277[data$item277 == 15]  <- 5

data$item278[data$item278 == 11]  <- 1
data$item278[data$item278 == 12]  <- 2
data$item278[data$item278 == 13]  <- 3
data$item278[data$item278 == 14]  <- 4
data$item278[data$item278 == 15]  <- 5

data$item279[data$item279 == 11]  <- 1
data$item279[data$item279 == 12]  <- 2
data$item279[data$item279 == 13]  <- 3
data$item279[data$item279 == 14]  <- 4
data$item279[data$item279 == 15]  <- 5

data$item280[data$item280 == 11]  <- 1
data$item280[data$item280 == 12]  <- 2
data$item280[data$item280 == 13]  <- 3
data$item280[data$item280 == 14]  <- 4
data$item280[data$item280 == 15]  <- 5

data$item281[data$item281 == 11]  <- 1
data$item281[data$item281 == 12]  <- 2
data$item281[data$item281 == 13]  <- 3
data$item281[data$item281 == 14]  <- 4
data$item281[data$item281 == 15]  <- 5

data$item282[data$item282 == 11]  <- 1
data$item282[data$item282 == 12]  <- 2
data$item282[data$item282 == 13]  <- 3
data$item282[data$item282 == 14]  <- 4
data$item282[data$item282 == 15]  <- 5

data$item283[data$item283 == 11]  <- 1
data$item283[data$item283 == 12]  <- 2
data$item283[data$item283 == 13]  <- 3
data$item283[data$item283 == 14]  <- 4
data$item283[data$item283 == 15]  <- 5

data$item284[data$item284 == 11]  <- 1
data$item284[data$item284 == 12]  <- 2
data$item284[data$item284 == 13]  <- 3
data$item284[data$item284 == 14]  <- 4
data$item284[data$item284 == 15]  <- 5

data$item285[data$item285 == 11]  <- 1
data$item285[data$item285 == 12]  <- 2
data$item285[data$item285 == 13]  <- 3
data$item285[data$item285 == 14]  <- 4
data$item285[data$item285 == 15]  <- 5

data$item286[data$item286 == 11]  <- 1
data$item286[data$item286 == 12]  <- 2
data$item286[data$item286 == 13]  <- 3
data$item286[data$item286 == 14]  <- 4
data$item286[data$item286 == 15]  <- 5

data$item287[data$item287 == 11]  <- 1
data$item287[data$item287 == 12]  <- 2
data$item287[data$item287 == 13]  <- 3
data$item287[data$item287 == 14]  <- 4
data$item287[data$item287 == 15]  <- 5

data$item288[data$item288 == 9]   <- 1
data$item288[data$item288 == 10]  <- 2
data$item288[data$item288 == 11]  <- 3
data$item288[data$item288 == 12]  <- 4
data$item288[data$item288 == 13]  <- 5

data$item289[data$item289 == 11]  <- 1
data$item289[data$item289 == 12]  <- 2
data$item289[data$item289 == 13]  <- 3
data$item289[data$item289 == 14]  <- 4
data$item289[data$item289 == 15]  <- 5

data$item290[data$item290 == 6]  <- 1
data$item290[data$item290 == 7]  <- 2
data$item290[data$item290 == 8]  <- 3
data$item290[data$item290 == 9]  <- 4
data$item290[data$item290 == 10] <- 5

data$item291[data$item291 == 6]  <- 1
data$item291[data$item291 == 7]  <- 2
data$item291[data$item291 == 8]  <- 3
data$item291[data$item291 == 9]  <- 4
data$item291[data$item291 == 10] <- 5

data$item292[data$item292 == 6]  <- 1
data$item292[data$item292 == 7]  <- 2
data$item292[data$item292 == 8]  <- 3
data$item292[data$item292 == 9]  <- 4
data$item292[data$item292 == 10] <- 5

data$item293[data$item293 == 6]  <- 1
data$item293[data$item293 == 7]  <- 2
data$item293[data$item293 == 8]  <- 3
data$item293[data$item293 == 9]  <- 4
data$item293[data$item293 == 10] <- 5

data$item294[data$item294 == 6]  <- 1
data$item294[data$item294 == 7]  <- 2
data$item294[data$item294 == 8]  <- 3
data$item294[data$item294 == 9]  <- 4
data$item294[data$item294 == 10] <- 5

data$item295[data$item295 == 6]  <- 1
data$item295[data$item295 == 7]  <- 2
data$item295[data$item295 == 8]  <- 3
data$item295[data$item295 == 9]  <- 4
data$item295[data$item295 == 10] <- 5

data$item296[data$item296 == 11]  <- 1
data$item296[data$item296 == 12]  <- 2
data$item296[data$item296 == 13]  <- 3
data$item296[data$item296 == 14]  <- 4
data$item296[data$item296 == 15]  <- 5

data$item297[data$item297 == 4]  <- 1
data$item297[data$item297 == 5]  <- 2
data$item297[data$item297 == 6]  <- 3
data$item297[data$item297 == 7]  <- 4
data$item297[data$item297 == 8]  <- 5

data$item298[data$item298 == 11]  <- 1
data$item298[data$item298 == 12]  <- 2
data$item298[data$item298 == 13]  <- 3
data$item298[data$item298 == 14]  <- 4
data$item298[data$item298 == 15]  <- 5

data$item299[data$item299 == 11]  <- 1
data$item299[data$item299 == 12]  <- 2
data$item299[data$item299 == 13]  <- 3
data$item299[data$item299 == 14]  <- 4
data$item299[data$item299 == 15]  <- 5

data$item300[data$item300 == 11]  <- 1
data$item300[data$item300 == 12]  <- 2
data$item300[data$item300 == 13]  <- 3
data$item300[data$item300 == 14]  <- 4
data$item300[data$item300 == 15]  <- 5

data$item301[data$item301 == 11]  <- 1
data$item301[data$item301 == 12]  <- 2
data$item301[data$item301 == 13]  <- 3
data$item301[data$item301 == 14]  <- 4
data$item301[data$item301 == 15]  <- 5

data$item302[data$item302 == 11]  <- 1
data$item302[data$item302 == 12]  <- 2
data$item302[data$item302 == 13]  <- 3
data$item302[data$item302 == 14]  <- 4
data$item302[data$item302 == 15]  <- 5

data$item303[data$item303 == 11]  <- 1
data$item303[data$item303 == 12]  <- 2
data$item303[data$item303 == 13]  <- 3
data$item303[data$item303 == 14]  <- 4
data$item303[data$item303 == 15]  <- 5

data$item304[data$item304 == 11]  <- 1
data$item304[data$item304 == 12]  <- 2
data$item304[data$item304 == 13]  <- 3
data$item304[data$item304 == 14]  <- 4
data$item304[data$item304 == 15]  <- 5

data$item305[data$item305 == 6]  <- 1
data$item305[data$item305 == 7]  <- 2
data$item305[data$item305 == 8]  <- 3
data$item305[data$item305 == 9]  <- 4
data$item305[data$item305 == 10] <- 5

data$item306[data$item306 == 6]  <- 1
data$item306[data$item306 == 7]  <- 2
data$item306[data$item306 == 8]  <- 3
data$item306[data$item306 == 9]  <- 4
data$item306[data$item306 == 10] <- 5

data$item307[data$item307 == 6]  <- 1
data$item307[data$item307 == 7]  <- 2
data$item307[data$item307 == 8]  <- 3
data$item307[data$item307 == 9]  <- 4
data$item307[data$item307 == 10] <- 5

## Attention check

data$item309[data$item309 == 16]  <- 1
data$item309[data$item309 == 17]  <- 2
data$item309[data$item309 == 18]  <- 3
data$item309[data$item309 == 19]  <- 4
data$item309[data$item309 == 20]  <- 5

data$item310[data$item310 == 6]  <- 1
data$item310[data$item310 == 7]  <- 2
data$item310[data$item310 == 8]  <- 3
data$item310[data$item310 == 9]  <- 4
data$item310[data$item310 == 10] <- 5

data$item311[data$item311 == 6]  <- 1
data$item311[data$item311 == 7]  <- 2
data$item311[data$item311 == 8]  <- 3
data$item311[data$item311 == 9]  <- 4
data$item311[data$item311 == 10] <- 5

data$item312[data$item312 == 6]  <- 1
data$item312[data$item312 == 7]  <- 2
data$item312[data$item312 == 8]  <- 3
data$item312[data$item312 == 9]  <- 4
data$item312[data$item312 == 10] <- 5

data$item313[data$item313 == 6]  <- 1
data$item313[data$item313 == 7]  <- 2
data$item313[data$item313 == 8]  <- 3
data$item313[data$item313 == 9]  <- 4
data$item313[data$item313 == 10] <- 5

data$item314[data$item314 == 6]  <- 1
data$item314[data$item314 == 7]  <- 2
data$item314[data$item314 == 8]  <- 3
data$item314[data$item314 == 9]  <- 4
data$item314[data$item314 == 10] <- 5

data$item315[data$item315 == 6]  <- 1
data$item315[data$item315 == 7]  <- 2
data$item315[data$item315 == 8]  <- 3
data$item315[data$item315 == 9]  <- 4
data$item315[data$item315 == 10] <- 5

data$item316[data$item316 == 16]  <- 1
data$item316[data$item316 == 17]  <- 2
data$item316[data$item316 == 18]  <- 3
data$item316[data$item316 == 19]  <- 4
data$item316[data$item316 == 20]  <- 5

data$item317[data$item317 == 6]  <- 1
data$item317[data$item317 == 7]  <- 2
data$item317[data$item317 == 8]  <- 3
data$item317[data$item317 == 9]  <- 4
data$item317[data$item317 == 10] <- 5

data$item318[data$item318 == 6]  <- 1
data$item318[data$item318 == 7]  <- 2
data$item318[data$item318 == 8]  <- 3
data$item318[data$item318 == 9]  <- 4
data$item318[data$item318 == 10] <- 5

data$item319[data$item319 == 6]  <- 1
data$item319[data$item319 == 7]  <- 2
data$item319[data$item319 == 8]  <- 3
data$item319[data$item319 == 9]  <- 4
data$item319[data$item319 == 10] <- 5

data$item320[data$item320 == 11] <- 1
data$item320[data$item320 == 12] <- 2
data$item320[data$item320 == 13] <- 3
data$item320[data$item320 == 14] <- 4
data$item320[data$item320 == 15] <- 5

data$item321[data$item321 == 11] <- 1
data$item321[data$item321 == 12] <- 2
data$item321[data$item321 == 13] <- 3
data$item321[data$item321 == 14] <- 4
data$item321[data$item321 == 15] <- 5

data$item322[data$item322 == 11] <- 1
data$item322[data$item322 == 12] <- 2
data$item322[data$item322 == 13] <- 3
data$item322[data$item322 == 14] <- 4
data$item322[data$item322 == 15] <- 5

data$item323[data$item323 == 11] <- 1
data$item323[data$item323 == 12] <- 2
data$item323[data$item323 == 13] <- 3
data$item323[data$item323 == 14] <- 4
data$item323[data$item323 == 15] <- 5

data$item324[data$item324 == 11] <- 1
data$item324[data$item324 == 12] <- 2
data$item324[data$item324 == 13] <- 3
data$item324[data$item324 == 14] <- 4
data$item324[data$item324 == 15] <- 5

data$item325[data$item325 == 11] <- 1
data$item325[data$item325 == 12] <- 2
data$item325[data$item325 == 13] <- 3
data$item325[data$item325 == 14] <- 4
data$item325[data$item325 == 15] <- 5

data$item326[data$item326 == 11] <- 1
data$item326[data$item326 == 12] <- 2
data$item326[data$item326 == 13] <- 3
data$item326[data$item326 == 14] <- 4
data$item326[data$item326 == 15] <- 5

data$item327[data$item327 == 11] <- 1
data$item327[data$item327 == 12] <- 2
data$item327[data$item327 == 13] <- 3
data$item327[data$item327 == 14] <- 4
data$item327[data$item327 == 15] <- 5

data$item328[data$item328 == 6]  <- 1
data$item328[data$item328 == 7]  <- 2
data$item328[data$item328 == 8]  <- 3
data$item328[data$item328 == 9]  <- 4
data$item328[data$item328 == 10] <- 5

data$item329[data$item329 == 11] <- 1
data$item329[data$item329 == 12] <- 2
data$item329[data$item329 == 13] <- 3
data$item329[data$item329 == 14] <- 4
data$item329[data$item329 == 15] <- 5

data$item330[data$item330 == 11] <- 1
data$item330[data$item330 == 12] <- 2
data$item330[data$item330 == 13] <- 3
data$item330[data$item330 == 14] <- 4
data$item330[data$item330 == 15] <- 5

data$item331[data$item331 == 6]  <- 1
data$item331[data$item331 == 7]  <- 2
data$item331[data$item331 == 8]  <- 3
data$item331[data$item331 == 9]  <- 4
data$item331[data$item331 == 10] <- 5

data$item332[data$item332 == 11] <- 1
data$item332[data$item332 == 12] <- 2
data$item332[data$item332 == 13] <- 3
data$item332[data$item332 == 14] <- 4
data$item332[data$item332 == 15] <- 5

data$item333[data$item333 == 11] <- 1
data$item333[data$item333 == 12] <- 2
data$item333[data$item333 == 13] <- 3
data$item333[data$item333 == 14] <- 4
data$item333[data$item333 == 15] <- 5

data$item334[data$item334 == 11] <- 1
data$item334[data$item334 == 12] <- 2
data$item334[data$item334 == 13] <- 3
data$item334[data$item334 == 14] <- 4
data$item334[data$item334 == 15] <- 5

data$item335[data$item335 == 11] <- 1
data$item335[data$item335 == 12] <- 2
data$item335[data$item335 == 13] <- 3
data$item335[data$item335 == 14] <- 4
data$item335[data$item335 == 15] <- 5

data$item336[data$item336 == 11] <- 1
data$item336[data$item336 == 12] <- 2
data$item336[data$item336 == 13] <- 3
data$item336[data$item336 == 14] <- 4
data$item336[data$item336 == 15] <- 5

data$item337[data$item337 == 18] <- 1
data$item337[data$item337 == 19] <- 2
data$item337[data$item337 == 20] <- 3
data$item337[data$item337 == 21] <- 4
data$item337[data$item337 == 22] <- 5

data$item338[data$item338 == 11] <- 1
data$item338[data$item338 == 12] <- 2
data$item338[data$item338 == 13] <- 3
data$item338[data$item338 == 14] <- 4
data$item338[data$item338 == 15] <- 5

data$item339[data$item339 == 11] <- 1
data$item339[data$item339 == 12] <- 2
data$item339[data$item339 == 13] <- 3
data$item339[data$item339 == 14] <- 4
data$item339[data$item339 == 15] <- 5

data$item340[data$item340 == 11] <- 1
data$item340[data$item340 == 12] <- 2
data$item340[data$item340 == 13] <- 3
data$item340[data$item340 == 14] <- 4
data$item340[data$item340 == 15] <- 5

data$item341[data$item341 == 11] <- 1
data$item341[data$item341 == 12] <- 2
data$item341[data$item341 == 13] <- 3
data$item341[data$item341 == 14] <- 4
data$item341[data$item341 == 15] <- 5

data$item342[data$item342 == 11] <- 1
data$item342[data$item342 == 12] <- 2
data$item342[data$item342 == 13] <- 3
data$item342[data$item342 == 14] <- 4
data$item342[data$item342 == 15] <- 5

data$item343[data$item343 == 11] <- 1
data$item343[data$item343 == 12] <- 2
data$item343[data$item343 == 13] <- 3
data$item343[data$item343 == 14] <- 4
data$item343[data$item343 == 15] <- 5

data$item344[data$item344 == 11] <- 1
data$item344[data$item344 == 12] <- 2
data$item344[data$item344 == 13] <- 3
data$item344[data$item344 == 14] <- 4
data$item344[data$item344 == 15] <- 5

data$item345[data$item345 == 11] <- 1
data$item345[data$item345 == 12] <- 2
data$item345[data$item345 == 13] <- 3
data$item345[data$item345 == 14] <- 4
data$item345[data$item345 == 15] <- 5

data$item346[data$item346 == 11] <- 1
data$item346[data$item346 == 12] <- 2
data$item346[data$item346 == 13] <- 3
data$item346[data$item346 == 14] <- 4
data$item346[data$item346 == 15] <- 5

data$item347[data$item347 == 11] <- 1
data$item347[data$item347 == 12] <- 2
data$item347[data$item347 == 13] <- 3
data$item347[data$item347 == 14] <- 4
data$item347[data$item347 == 15] <- 5

data$item348[data$item348 == 11] <- 1
data$item348[data$item348 == 12] <- 2
data$item348[data$item348 == 13] <- 3
data$item348[data$item348 == 14] <- 4
data$item348[data$item348 == 15] <- 5

data$item349[data$item349 == 11] <- 1
data$item349[data$item349 == 12] <- 2
data$item349[data$item349 == 13] <- 3
data$item349[data$item349 == 14] <- 4
data$item349[data$item349 == 15] <- 5

data$item350[data$item350 == 11] <- 1
data$item350[data$item350 == 12] <- 2
data$item350[data$item350 == 13] <- 3
data$item350[data$item350 == 14] <- 4
data$item350[data$item350 == 15] <- 5

data$item351[data$item351 == 11] <- 1
data$item351[data$item351 == 12] <- 2
data$item351[data$item351 == 13] <- 3
data$item351[data$item351 == 14] <- 4
data$item351[data$item351 == 15] <- 5

data$item352[data$item352 == 11] <- 1
data$item352[data$item352 == 12] <- 2
data$item352[data$item352 == 13] <- 3
data$item352[data$item352 == 14] <- 4
data$item352[data$item352 == 15] <- 5

data$item353[data$item353 == 11] <- 1
data$item353[data$item353 == 12] <- 2
data$item353[data$item353 == 13] <- 3
data$item353[data$item353 == 14] <- 4
data$item353[data$item353 == 15] <- 5

data$item354[data$item354 == 21] <- 1
data$item354[data$item354 == 22] <- 2
data$item354[data$item354 == 23] <- 3
data$item354[data$item354 == 24] <- 4
data$item354[data$item354 == 25] <- 5

data$item355[data$item355 == 11] <- 1
data$item355[data$item355 == 12] <- 2
data$item355[data$item355 == 13] <- 3
data$item355[data$item355 == 14] <- 4
data$item355[data$item355 == 15] <- 5

data$item356[data$item356 == 11] <- 1
data$item356[data$item356 == 12] <- 2
data$item356[data$item356 == 13] <- 3
data$item356[data$item356 == 14] <- 4
data$item356[data$item356 == 15] <- 5

data$item357[data$item357 == 11] <- 1
data$item357[data$item357 == 12] <- 2
data$item357[data$item357 == 13] <- 3
data$item357[data$item357 == 14] <- 4
data$item357[data$item357 == 15] <- 5

data$item358[data$item358 == 11] <- 1
data$item358[data$item358 == 12] <- 2
data$item358[data$item358 == 13] <- 3
data$item358[data$item358 == 14] <- 4
data$item358[data$item358 == 15] <- 5

data$item359[data$item359 == 11] <- 1
data$item359[data$item359 == 12] <- 2
data$item359[data$item359 == 13] <- 3
data$item359[data$item359 == 14] <- 4
data$item359[data$item359 == 15] <- 5

data$item360[data$item360 == 11] <- 1
data$item360[data$item360 == 12] <- 2
data$item360[data$item360 == 13] <- 3
data$item360[data$item360 == 14] <- 4
data$item360[data$item360 == 15] <- 5

data$item361[data$item361 == 11] <- 1
data$item361[data$item361 == 12] <- 2
data$item361[data$item361 == 13] <- 3
data$item361[data$item361 == 14] <- 4
data$item361[data$item361 == 15] <- 5

data$item362[data$item362 == 11] <- 1
data$item362[data$item362 == 12] <- 2
data$item362[data$item362 == 13] <- 3
data$item362[data$item362 == 14] <- 4
data$item362[data$item362 == 15] <- 5

data$item363[data$item363 == 11] <- 1
data$item363[data$item363 == 12] <- 2
data$item363[data$item363 == 13] <- 3
data$item363[data$item363 == 14] <- 4
data$item363[data$item363 == 15] <- 5

data$item364[data$item364 == 11] <- 1
data$item364[data$item364 == 12] <- 2
data$item364[data$item364 == 13] <- 3
data$item364[data$item364 == 14] <- 4
data$item364[data$item364 == 15] <- 5

data$item365[data$item365 == 11] <- 1
data$item365[data$item365 == 12] <- 2
data$item365[data$item365 == 13] <- 3
data$item365[data$item365 == 14] <- 4
data$item365[data$item365 == 15] <- 5

data$item366[data$item366 == 11] <- 1
data$item366[data$item366 == 12] <- 2
data$item366[data$item366 == 13] <- 3
data$item366[data$item366 == 14] <- 4
data$item366[data$item366 == 15] <- 5

data$item367[data$item367 == 11] <- 1
data$item367[data$item367 == 12] <- 2
data$item367[data$item367 == 13] <- 3
data$item367[data$item367 == 14] <- 4
data$item367[data$item367 == 15] <- 5

data$item368[data$item368 == 11] <- 1
data$item368[data$item368 == 12] <- 2
data$item368[data$item368 == 13] <- 3
data$item368[data$item368 == 14] <- 4
data$item368[data$item368 == 15] <- 5

data$item369[data$item369 == 11] <- 1
data$item369[data$item369 == 12] <- 2
data$item369[data$item369 == 13] <- 3
data$item369[data$item369 == 14] <- 4
data$item369[data$item369 == 15] <- 5

data$item370[data$item370 == 11] <- 1
data$item370[data$item370 == 12] <- 2
data$item370[data$item370 == 13] <- 3
data$item370[data$item370 == 14] <- 4
data$item370[data$item370 == 15] <- 5

data$item371[data$item371 == 11] <- 1
data$item371[data$item371 == 12] <- 2
data$item371[data$item371 == 13] <- 3
data$item371[data$item371 == 14] <- 4
data$item371[data$item371 == 15] <- 5

data$item372[data$item372 == 11] <- 1
data$item372[data$item372 == 12] <- 2
data$item372[data$item372 == 13] <- 3
data$item372[data$item372 == 14] <- 4
data$item372[data$item372 == 15] <- 5

```


```{r scales}

## Study 2 DVs

data$item387      <- 7- data$item387           ## only reflected engagement item

data$absorption   <- rowMeans(data[c(380:386)], na.rm=TRUE)
data$vigor        <- rowMeans(data[c(387:392)], na.rm=TRUE) 
data$dedication   <- rowMeans(data[c(393:399)], na.rm=TRUE) 

data$cognitive    <- rowMeans(data[c(380:382, 387:388, 393:395)], na.rm=TRUE)
data$affective    <- rowMeans(data[c(383:384, 389:390, 396:397)], na.rm=TRUE) 
data$behavioral   <- rowMeans(data[c(385:386, 391:392, 398:399)], na.rm=TRUE) 

######################################################

data$burnout      <- rowMeans(data[c(373:376)], na.rm=TRUE)
data$stress       <- rowMeans(data[c(377:379)], na.rm=TRUE)
data$engagement   <- rowMeans(data[c(380:399)], na.rm=TRUE)        ## added 10/12 because analyses too wonky with 3 subscales

alpha.abs <- psych::alpha(data[c(380:386)])
alpha.vig <- psych::alpha(data[c(387:392)])
alpha.ded <- psych::alpha(data[c(393:399)])
alpha.eng <- psych::alpha(data[c(380:399)])

alpha.bur <- psych::alpha(data[c(373:376)])
alpha.str <- psych::alpha(data[c(377:379)])

```

## Materials  

### Characteristics, Demands, and Resources  

Our analyses are organized by O\*NET's classifications of "work activity": 1) *Information Input* (5 statements), 2) *Interacting with Others* (17 statements), 3) *Mental Processes* (10 statements), and 4) *Work Output* (9 statements) and "work context": 5) *Interpersonal Relationships* (14 statements), 6) *Physical Work Conditions* (30 statements)[^footie], and 7) *Structural Job Characteristics* (13 statements).  

Other than very minor grammatical editing (for example, changing "the" to "you"), we retained the O\*NET wording for our item stems. We also administered O\*NET's response scales, several of which were unique across items. Subsequent to these descriptions of the respondent's work activity and context, each respondent who agreed that an element had *at least some relevance to their job* was also asked to rate that element in terms of, 1) ...this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) ...this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) ...this aspect of your job is a hinderance that can inhibit personal growth, learning, and work goal attainment. Our analyses focus on the extent to which the O\*NET work characteristics are viewed as resources, challenges, or hindrances. 

[^footie]:Note that we excluded several statements within the "Physical Work Conditions" ratings of resources and demands (for example, we did not ask if "exposure to radiation" was considered a demand or resource). In total there were 11 exclusions from this category when assessing demands and resources. 

```{r ONETclass}

data$onet.resource.ii <- rowMeans(data[c(162:166)], na.rm=TRUE)
data$onet.resource.mp <- rowMeans(data[c(167:176)], na.rm=TRUE)
data$onet.resource.wo <- rowMeans(data[c(177:185)], na.rm=TRUE)
data$onet.resource.io <- rowMeans(data[c(186:202)], na.rm=TRUE)
data$onet.resource.ir <- rowMeans(data[c(149:161)], na.rm=TRUE)
data$onet.resource.pc <- rowMeans(data[c(128:144,146:148)], na.rm=TRUE)
data$onet.resource.sc <- rowMeans(data[c(118:127)], na.rm=TRUE)

overall.resource <- rowMeans(data[c(118:144,147:202)], na.rm=TRUE)

data$onet.hindrance.ii <- rowMeans(data[c(246:247,249:252)], na.rm=TRUE)
data$onet.hindrance.mp <- rowMeans(data[c(252:261)], na.rm=TRUE)
data$onet.hindrance.wo <- rowMeans(data[c(262:270)], na.rm=TRUE)
data$onet.hindrance.io <- rowMeans(data[c(271:287)], na.rm=TRUE)
data$onet.hindrance.ir <- rowMeans(data[c(233:245)], na.rm=TRUE)
data$onet.hindrance.pc <- rowMeans(data[c(213:232)], na.rm=TRUE)
data$onet.hindrance.sc <- rowMeans(data[c(203:212)], na.rm=TRUE)

overall.hindrance <- rowMeans(data[c(203:247,249:287)], na.rm=TRUE)

data$onet.challenge.ii <- rowMeans(data[c(332:336)], na.rm=TRUE)
data$onet.challenge.mp <- rowMeans(data[c(337:346)], na.rm=TRUE)
data$onet.challenge.wo <- rowMeans(data[c(347:355)], na.rm=TRUE)
data$onet.challenge.io <- rowMeans(data[c(356:372)], na.rm=TRUE)
data$onet.challenge.ir <- rowMeans(data[c(319:331)], na.rm=TRUE)
data$onet.challenge.pc <- rowMeans(data[c(298:307,309:318)], na.rm=TRUE)
data$onet.challenge.sc <- rowMeans(data[c(288:297)], na.rm=TRUE)

overall.challenge <- rowMeans(data[c(288:307,309:372)], na.rm=TRUE)

```

### Burnout and Stress  

Were taken from the Copenhagen Psychosocial Questionnaire [@burr_third_2019]. There were 4 burnout items and 3 stress items with current sample $\alpha$'s of `r round(alpha.bur$total$raw_alpha,2)` (burnout) and `r round(alpha.str$total$raw_alpha,2)` (stress).
 
### Engagement

The 18-item engagement measure was recently developed [@engage_2022], with the authors specifying three subscales which yielded current sample $\alpha$'s of `r round(alpha.abs$total$raw_alpha,2)` (Absorption) and `r round(alpha.vig$total$raw_alpha,2)` (Vigor), and `r round(alpha.ded$total$raw_alpha,2)` (Dedication). For the purposes of the current study, we focused on an overall engagement score (18 item aggregate, $\alpha$ = `r round(alpha.eng$total$raw_alpha,2)`). 

# Results

Our analyses are grouped by characteristics of work that are percieved as being resources, challenge demands, and hindrance demands.

### Resources

Across all items, the average perception that an O\*NET job element could be considered a *resource* was `r round(mean(overall.resource, na.rm=TRUE),2)` with a standard deviation of `r round(sd(overall.resource, na.rm=TRUE),2)`.

```{r resourcesregs, eval=FALSE}

engage.res <- lm(engagement ~ onet.resource.ii+onet.resource.mp+onet.resource.wo+onet.resource.io+onet.resource.ir+onet.resource.pc+onet.resource.sc, data)

burnout.res <- lm(burnout ~ onet.resource.ii+onet.resource.mp+onet.resource.wo+onet.resource.io+onet.resource.ir+onet.resource.pc+onet.resource.sc, data)

stress.res <- lm(stress ~ onet.resource.ii+onet.resource.mp+onet.resource.wo+onet.resource.io+onet.resource.ir+onet.resource.pc+onet.resource.sc, data)

library(apaTables)

apa.reg.table(engage.res, filename="engage.resource.doc")
apa.reg.table(burnout.res, filename="burnout.resource.doc")
apa.reg.table(stress.res, filename="stress.resource.doc")

```

The more a work characteristic was perceived as a resource, the more engaged the respondent was ($R^2$ = .15, $F_(7,528)$ = 12.82, *p* < .001), although there was a only a trivial effect between being viewed as a resource and stress ($R^2$ = .03, $F_(7,528)$ = 2.20, *p* < .05) and no significant association between being viewed as a resource and burnout ($R^2$ = .01, $F_(7,528)$ = 1.12, *p* = .35). Note that this is consistent with the predictions of the JD-R. 

### Hindrances

Across all items, the average perception that an O\*NET job element could be considered a *hindrance* was `r round(mean(overall.hindrance, na.rm=TRUE),2)` with a standard deviation of `r round(sd(overall.hindrance, na.rm=TRUE),2)`.

```{r hindrancesregs, eval=FALSE}

engage.hin <- lm(engagement ~ onet.hindrance.ii+onet.hindrance.mp+onet.hindrance.wo+onet.hindrance.io+onet.hindrance.ir+onet.hindrance.pc+onet.hindrance.sc, data)

burnout.hin <- lm(burnout ~ onet.hindrance.ii+onet.hindrance.mp+onet.hindrance.wo+onet.hindrance.io+onet.hindrance.ir+onet.hindrance.pc+onet.hindrance.sc, data)

stress.hin <- lm(stress ~ onet.hindrance.ii+onet.hindrance.mp+onet.hindrance.wo+onet.hindrance.io+onet.hindrance.ir+onet.hindrance.pc+onet.hindrance.sc, data)

apa.reg.table(engage.hin, filename="engage.hindrance.doc")
apa.reg.table(burnout.hin, filename="burnout.hindrance.doc")
apa.reg.table(stress.hin, filename="stress.hindrance.doc")

```

There was a marginal association between a work characteristic being percieved as a greater hindrance and lower levels of engagement ($R^2$ = .07, $F_(7,528)$ = 5.84, *p* < .001), with similar effects both between being viewed as a hindrance and increased stress ($R^2$ = .06, $F_(7,528)$ = 4.88, *p* < .001) as well as increased levels of burnout ($R^2$ = .06, $F_(7,528)$ = 4.90, *p* < .001). 

### Challenges

Across all items, the average perception that an O\*NET job element could be considered a *challenge* was `r round(mean(overall.challenge, na.rm=TRUE),2)` with a standard deviation of `r round(sd(overall.challenge, na.rm=TRUE),2)`.

```{r challengesregs, eval=FALSE}

engage.cha <- lm(engagement ~ onet.challenge.ii+onet.challenge.mp+onet.challenge.wo+onet.challenge.io+onet.challenge.ir+onet.challenge.pc+onet.challenge.sc, data)

burnout.cha <- lm(burnout ~ onet.challenge.ii+onet.challenge.mp+onet.challenge.wo+onet.challenge.io+onet.challenge.ir+onet.challenge.pc+onet.challenge.sc, data)

stress.cha <- lm(stress ~ onet.challenge.ii+onet.challenge.mp+onet.challenge.wo+onet.challenge.io+onet.challenge.ir+onet.challenge.pc+onet.challenge.sc, data)


apa.reg.table(engage.cha, filename="engage.challenge.doc")
apa.reg.table(burnout.cha, filename="burnout.challenge.doc")
apa.reg.table(stress.cha, filename="stress.challenge.doc")

```

The impact of challenging demands on engagement was similar in direction and magnitude to that of resources, as consistent with JD-R predictions ($R^2$ = .13, $F_(7,528)$ = 11.03, *p* < .001), with absent effects for both stress ($R^2$ = .01, $F_(7,528)$ = 0.88, *p* = .52) and burnout ($R^2$ = .02, $F_(7,528)$ = 1.21, *p* = .30; that is, workplace challenges were predictive of engagement but not self-reported stress or burnout). 

## Summary

```{r itemlevel}

engage.resource.items.1 <- lm(engagement ~ item118+item119+item120+item121+item122+item123+item124+item125+item126+item127, data)

engage.resource.items.2 <- lm(engagement ~ item118+item119+item120+item121+item122+item123+item124+item125+item126+item127+
                                 item86+item187+item188+item189+item190+item191+item192+item193+item194+item195+item196+item197+item198+item199+item200+item201+item202, data)

engage.resource.items.3 <- lm(engagement ~ item118+item119+item120+item121+item122+item123+item124+item125+item126+item127+
                                 item86+item187+item188+item189+item190+item191+item192+item193+item194+item195+item196+item197+item198+item199+item200+item201+item202+item149+item150+item151+item152+item153+item154+item155+item156+item157+item158+item159,data)


## Note: 1=Structural job characteristics, 2=Interacting with others, 3=Interpersonal relationships
## Doesn't work too many missing values


```

Looking a little less coarsely at our two strongest associations, we explored individual element contributions to the prediction of engagement for our strongest challenges and resources (structural job characteristics, interacting with others, and interpersonal relationships) applying a series of hierarchical regressions.  

The full correlation table including a simultaneous presentation of resources, challenges, and demands is too large, but we did investigate associations among these characteristics, with the average correlation among average correlation among resources and challenges being .37 (sd=.16), resources and hindrances being -.16 (sd=.08), and average correlation among challenges and hindrances being -.13 (sd=.09). 

```{r correlationsresource}

r <- corx::corx(data[,c(413, 411:412, 414:420)],                     ## can extend if needed
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table
                  caption = "Scale intercorrelations (resources).",
                  note = "* p < 0.05; ** p < 0.01; *** p < 0.001",
                  landscape = TRUE,
                  escape = F)

```


```{r correlationschallenge}

r <- corx::corx(data[,c(413, 411:412, 428:434)],                     ## can extend if needed
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table
                  caption = "Scale intercorrelations (challenges).",
                  note = "* p < 0.05; ** p < 0.01; *** p < 0.001",
                  landscape = TRUE,
                  escape = F)

```


```{r correlationshindrance}

r <- corx::corx(data[,c(413, 411:412, 421:427)],                     ## can extend if needed
                triangle = "lower",
                stars = c(0.05, 0.01, 0.001),
                describe = c(`$M$` = mean, `$SD$` = sd))

papaja::apa_table(r$apa, # apa contains the data.frame needed for apa_table
                  caption = "Scale intercorrelations (hindrances).",
                  note = "* p < 0.05; ** p < 0.01; *** p < 0.001",
                  landscape = TRUE,
                  escape = F)

```



# Discussion

There is richer information available within this dataset. Our job elements are grouped by O\*NET category, which facilitates broad exploration, however, individual elements likely impact engagement, stress, and burnout, so these individual elements should be explored. For example, the *Work Context* element of "having to meet strict deadlines" is likely something that is important alone. Incremental variance couldn't look at because of sheer number of IVs.

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
